Predictors of frog survival following translocations - analyses

### 2022-10-25 code/translocation_survival_analysis.Rmd
Address #4, provide an example of a flat prior on lines 90-110

>>>>

## Explore a flat prior

We can explore a flat prior on the intercept using the code below.

```{r}
m1_flat <- stan_glm(
  surv ~ length + snow_t + snow_t1 + day + bdload_l + elevation + first + male + donor,
  data = d1,
  family = binomial,
  prior_intercept=NULL,
  chains = 4, 
  iter = 5000*2,
  cores = 4,
  seed = 84735)

# Confirm our prior is flat
prior_summary(m1_flat)

# Notice that the estimate of the intercept is unchanged between the two models
m1_flat
m1a
```
